Project Thesis/Report

### 2022-01-10 Gandhi_Project_Report/draft3.tex
Clifford, Thomas mostly done. USP discussion done. Working on introducing H2

\usepackage{enumitem}
\usepackage{multirow}

@@

\begin{Definition}
  [\bf Flow of an Equation] \label{Dfn_Flow}
  The flow of the equation  $\dot{x} = f(x)$  is defined to be a mapping $\varphi: \mathbb{R}^n \times \mathbb{R} \to \mathbb{R}$ where $\varphi(x_0,t)= x(t)$ for the solution $x(t)$ with $x(0)=x_0$ 
\end{Definition}

@@

A core concept in the study of dynamical systems is that of invariance. 
\begin{Definition}
  [\bf Invariant Set] \label{Dfn_InvariantSet}
  Given a discrete-time dynamical system $T: U \to U$, a subset $A \subset U$ is said to be an \emph{invariant set} if $T(A) =A$. 
\end{Definition}

We also define the orbit of a function $T$.
\begin{Definition}
  [\bf Orbit of $T$] \label{Dfn_Orbit}
  The orbit of $T$ is to be defined the sequence $\bar{u} = \{u_n\}_{n\in \mathbb{Z}}$ obeying the update equation, $u_{n+1}=Tu_n$, $n \in \mathbb{Z}$. 
\end{Definition}

@@

\begin{Definition} 
  [\bf Attractor] \label{Dfn_Attractor}
  Let $T: U \to U$, where $U$  is a metric space with metric $d$. A compact subset $A \subset U$ is said to be an attractor if it satisfies the three conditions: 
  \vspace{-8mm}
  \begin{enumerate}
	\item $A$ is invariant. 
	\item $A$ is asymptotically stable, i.e., for every $\epsilon > 0$ and for all $u$ so that $d(u,A) < \epsilon$, we have $d(T^nu,A) \to 0$ as $n\to \infty$. 
	\item $A$ has Lyapunov stability, i.e., for every $\epsilon > 0$  there exists a $\delta(\epsilon) > 0$ so that $d(u,A) < \delta$ implies $d(T^nu,A) < \epsilon$ for all $n\ge 0$.  
\end{enumerate}
\end{Definition}

@@

\begin{Definition}
  [\bf {Sensitive Dependence on Initial Conditions}] \label{Dfn_SDIC}
A dynamical system $T: U \to U$ is said to have sensitive dependence on initial conditions (SDIC) if there exists a $\delta > 0$ such that for every $u \in U$ and in every neighborhood of $u \in U$ there exists a $v\in{U}$ and an integer $N:=N{(u,v)}\in\mathbb{Z}$ such that $d(T^Nu,T^Nv)>\delta$. 	
\end{Definition}

@@

\begin{Definition}
  [\bf {Topologically Transitive}] \label{Dfn_TopTrans}
	A dynamical system $F: U \to U$ is topologically transitive if for any pair of nonempty open sets $E_1$ and $E_2$ there exists a $n\in\mathbb{N}$ such that $T^n(E_1) \cap E_2 \not= \emptyset$. 
\end{Definition}

@@

\begin{Definition} 
  [\bf {Meager Set}] \label{Dfn_Meager Set}
A subset of a topological space $U$ is said to be a meager set if it can be written as a countable union of sets of with empty interior. The complement of the a meager set is set to be a residual set.
\end{Definition}

@@

We may now define the notion of Chaos as formulated by Devaney\cite{devaney2018introduction}.
\begin{Definition}
  [\bf {Devaney's Chaos}]\label{Dfn_ChaosDec}
	A dynamical system $T: U \to U$ is said to exhibit chaos in the sense of Devaney if it satisfies the three properties:
	\vspace{-5mm}
  \begin{enumerate}
		\item $T$ has SDIC.
		\item $T$ is topologically transitive.
		\item The set of periodic points of $T$ are dense in $U$. 
	\end{enumerate}
\end{Definition}

@@

\begin{Definition}  
  [\bf {Conjugacy \& Semi-Conjugacy}]\label{Dfn_Conjugate}
  Consider the dynamical systems $T:U\to{U}$, $S:V\to{V}$ and suppose the relationship $\phi \circ T=S\circ \phi$ holds. If $\phi:U\to{V}$ is a homeomorphism, then $S$ is said to be conjugate to $T$ and $\phi$ is called a conjugacy. If we relax the criterion on $\phi$ and merely require $\phi$ to be continuous and surjective where $\phi:U\to{V}$, then $\phi$ is a semi-conjugacy between $T$ and $S$ where T has domain $U$ and S has domain $V$; S is said to be semi-conjugate to T. 
\end{Definition}

@@

We define first the concepts of homeomorphism and embedding:
\begin{Definition}
  [\bf {Homeomorphism}]\label{Dfn_homeo}
  A homeomorphism is a function $f:Z\rightarrow Y$ between two topological spaces $Z$ and $Y$ that is continuous, bijective and has a continuous inverse. 
\end{Definition}

\begin{Definition}
  [\bf {Embedding}]\label{Dfn_embed}
  Consider a homeomorphism $f:Z\rightarrow Y$ for $Y\subset X$. $Z$ is said to be embedded in $X$ by $f$.
\end{Definition}

@@

% \ednote{M: You can omit the theorem, and just say it is a uniform attractor in the nonautonomous dynamical systems literature \cite{Manju_Nonlinearity}, and say the discussion on nonautonomous attractors is beyond the scope of the thesis.}
\textbf{NEED TO PARAPHRASE}
\newline In our context, $g$ having the USP is equivalent to $g$ being a topological contraction \cite{manjunath2021universal}, or alternatively that $g$ exhibits the Echo State Property(ESP). 
In \cite{Manju_ESP} the echo state property is a key for the design and training of recurrent neural networks within the paradigm of reservoir computing.
Available definitions and theorems concerning the echo state property, however, are of little practical use because they do not relate the network response to temporal or statistical properties of the driving input.

A greater discussion is presented in \cite{jaeger2001echo}
a particular stability concept for which a number of equivalent definitions are available \cite{jaeger2001echo}.

In most of the reservoir computing (RC) literature, the idea of memory-loss or fading memory popularly called
the echo state property (ESP) is treated as a stability property of the system valid
for all inputs. In such a case, the ESP guarantees that the entire past history of the
input determines the state of the system precisely, i.e., there is no possibility of two
or more reachable states at any given point in time [5] if the entire past values of the
input have influenced the dynamics. The formal definition linking ESP intrinsically
to an input is available in [4].

In the context of information processing, when a driven system g has a causal em-
bedding, it helps carry over any input ū onto the solution space without distortion or
loss of information. This is a very important feature, and the current discrete-time
state space models used in reservoir computing do not exploit the causal embedding.
We intend to demonstrate the utility of these theoretical results in a future work
directed at applications.

For natural systems, say, for instance, when the human brain is viewed as a driven
system where a time-varying external stimulus (for instance, a visual stimulus) is
an input, the input can be causally embedded into the nervous system without the
need for a particular structure that is custom-made for each stimulus as long as
the system has the USP. From the perspective of perturbation of an autonomous
dynamical system, if the resulting nonautonomous system has the USP, then the
temporal structure of noise relates to the dynamics on a nonautonomous uniform
attractor through a topological semi-conjugacy or a conjugacy.

The continuity of E reflects on whether small changes in u ~ would result in a ‘propor-
tionate’ response in the solution space – a notion of input related stability as defined in \cite{Manju_ESP}

To understand how solutions become sensitive to a perturbation of the input for systems without USP, we define a stability notion that describes how the collection of all solutions obtained from an input ū are mapped onto the solution space.

Sufficient to consider continuity of encoding map.

owing to the USP of the driven system $g$ one gains input-related, parameter-related stability \cite{manjunath2020stability}

Historically, data have been transformed into a different space for processing to gain some advantages. For example, according to Vapnik–Chervonenkis theory (e.g., [16]) mapping data into a higher dimension often provides much greater classification power. 
Mapping temporal data through a delay-coordinate mapping in Takens delay embedding uncovers hidden information [17]. In data-driven modeling employing Koopman’s theory (e.g., [18]–[20]), 
approximating the dynamics of a dynamical system through a linear dynamicalsystem in a higher dimensional space is often possible by mapping the data samplewise into the higher dimensional space

we first note that when T is not invertible, the dynamics of (U, T ) is only topologically semi-conjugate to $(\hat{U}, \hat{T})$ and hence the dynamics in $(\hat{U}, \hat{T})$ could have additional complexity.

xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx

Having already defined the reachable set $X_U$, we pause for a moment to fix additional notation.
Letting $\cev{u}^{n}:=(\ldots,u_{n-2} ,u_{n-1})$ be the left-infinite subsequence of an input, $\overleftarrow{U}$ then denotes all these left-infinite sequences in $U$. 
Moreover, $\cev{u}^{n}v:=(\ldots,u_{n-2} ,u_{n-1}, v)$ is to symbolise the input up to time $n$ with $v \in U$ being the specific input value at time $n$. 
The introduction of a new input at time $n$ can be described by a mapping $\sigma_v:   \cev{u}^{n} \mapsto \cev{u}^{n}v$.

@@

  Restricting our attention more and more, we now consider a specific subclass of conjugacies.

@@

\textbf{make special note of a} %\ednote{something you want to fill?} }
\begin{Definition}
  [\bf Causal Mapping]\label{Def_CausMap}
  A continuous, surjective map $H:\overleftarrow{U}\to\overleftarrow{X}_U$ such that \[H\circ\tilde{g}_v=\sigma\circ{H}\] where $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
\end{Definition}

@@

\textbf{When considering the map $H$, we once again restrict our focus of $H$ to the function $H_2(\overline{u}):=(h(r\overline{u}, h(\overline{u})))$. }

@@

\section{Numerical simulations}
\subsection{Double Pendulum}

@@

This system has four variables: angle and angular velocity of each pendulum rod. An ideal system is assumed where the rods are massless and no friction in the pivots are considered.
The scalar equations of motion are derived using Newtonian physics and can be found in \cite{DPFormulas}. The second-order system is converted to a first-order ODE and solved using the Runge-Kutta numerical method.

@@

\begin{itemize}
\item Thomas:
\begin{eqnarray}\label{eqns_thomas}
  u_x = \sin(y) - \beta{x} \\
  u_y = \sin(z) - \beta{y} \\
  u_z = \sin(x) - \beta{z}
\end{eqnarray}

\item Clifford:
\begin{equation}\label{eqn_clifford}
  \frac{\sin(ay) + c\cos(ax)}{\sin(bx)+d\cos(by)}
\end{equation}
\end{itemize}

One is easily reminded of the Lorenz system, another three-equation deterministic model which exhibits chaotic behaviour.

\section{Generalized Pearson correlation coefficient for the DP and other attractors}

\textbf{Insert table: D.Pendulum, Lorenz, Others (Clifford \& Thomas)}

@@

          \hline
          $(w_n)$ comes from the Clifford Attractor \\ (for $a = -1.7; b = 1.8; c = -1.9; d = -0.4$): & & & \\
        {$w_{n+1}= \begin{bmatrix} \sin(aw_{n,y}) + c\cos(aw_{n,x}) \\ 
                                                                    \sin(bw_{n,x})+d\cos(bw_{n,y}) \end{bmatrix}$} & & & \\
          \multirow{3}{*}{$u_n = w_n-\overline{w}$}
              & 10 & -0.21713 & 0.78719 \\
              & 100 & &  0.8334 \\
              & 1000 & & 0.84854 \\
          \hline

          \hline 
          $(w_n)$ comes from the Logistic map: & & & \\
          {$ w_{n+1}  = 4w_n(1-w_n)$} & & & \\
          \multirow{3}{*}{$u_n = w_n - 0.5$} 
              & 10 &-0.0314  & 0.5577\\
              & 100 &  & 0.7150\\
              & 1000 & & 0.7826\\
          \hline

          \hline
          $(w_n)$ comes from the Svensson Attractor \\ (for $a = -1.7; b = 1.8; c = -1.9; d = -0.4$): & & & \\
          {$w_{n+1}= \begin{bmatrix} d\sin(aw_{n,x}) - \sin(bw_{n,y}) \\ 
                                                                      c\cos(aw_{n,x})+\cos(bw_{n,y}) \end{bmatrix}$} & & & \\
            \multirow{3}{*}{$u_n = w_n-\overline{w}$}
                & 10 & -0.2243 & 0.49698 \\
                & 100 & &  0.63310 \\
                & 1000 & & 0.71151 \\
          \hline

      \end{tabular}} %\ednote{http://paulbourke.net/fractals/peterdejong/}

      \caption{Multidimensional Correlation Coefficients $\rho$ to indicate a general reduction in the functional complexity of the map $G_T$ that arises from a RNN. Each row corresponds to a different dynamical system used in the experiments in \cite{Main_article}. In the second column corresponds to the dimension of $X$ (number of artificial neurons) in the RNN used. 
      The numerical estimate of $\rho$ for the relevant vectors is plotted in the last two columns. The reader can compare the linear relationship between $u_n$ vs $T(u_{n})$ and the linear relationship $\begin{bmatrix}
              x_{n-1}\\
              x_n
          \end{bmatrix}$ vs $G_T \left( \begin{bmatrix}
              x_{n-1}\\
              x_n
          \end{bmatrix}\right)$. The dimension of the RNN from \eqref{Seq_RNN} is also given, showcasing that increasing the dimension of the driven system typically yields a map $G_T$ of lower functional complexity.} \label{Table_FC}
      \end{table}
  \end{center}

>>>>

\usepackage{enumitem}
\usepackage{multirow}
\usepackage{longtable}
\usepackage[export]{adjustbox}

@@

\begin{Definition}
  [\bf Flow of an Equation] \label{Dfn_Flow}\rm
  The flow of the equation  $\dot{x} = f(x)$  is defined to be a mapping $\varphi: \mathbb{R}^n \times \mathbb{R} \to \mathbb{R}$ where $\varphi(x_0,t)= x(t)$ for the solution $x(t)$ with $x(0)=x_0$ 
\end{Definition}

@@

A core concept in the study of dynamical systems is that of invariance. 
\begin{Definition}
  [\bf Invariant Set]\label{Dfn_InvariantSet}\rm
  Given a discrete-time dynamical system $T: U \to U$, a subset $A \subset U$ is said to be an \emph{invariant set} if $T(A) =A$. 
\end{Definition}

We also define the orbit of a function $T$.
\begin{Definition}
  [\bf Orbit of $T$]\label{Dfn_Orbit}\rm
  The orbit of $T$ is to be defined the sequence $\bar{u} = \{u_n\}_{n\in \mathbb{Z}}$ obeying the update equation, $u_{n+1}=Tu_n$, $n \in \mathbb{Z}$. 
\end{Definition}

@@

\begin{Definition}
  [\bf Attractor]\label{Dfn_Attractor}\rm
  Let $T: U \to U$, where $U$  is a metric space with metric $d$. A compact subset $A \subset U$ is said to be an attractor if it satisfies the three conditions: 
  \vspace{-8mm}
  \begin{enumerate}
	\item $A$ is invariant. 
	\item $A$ is asymptotically stable, i.e., for every $\epsilon > 0$ and for all $u$ so that $d(u,A) < \epsilon$, we have $d(T^nu,A) \to 0$ as $n\to \infty$. 
	\item $A$ has Lyapunov stability, i.e., for every $\epsilon > 0$  there exists a $\delta(\epsilon) > 0$ so that $d(u,A) < \delta$ implies $d(T^nu,A) < \epsilon$ for all $n\ge 0$.  
\end{enumerate}
\end{Definition}

@@

\begin{Definition}\rm
  [\bf {Sensitive Dependence on Initial Conditions}]\label{Dfn_SDIC}\rm
A dynamical system $T: U \to U$ is said to have sensitive dependence on initial conditions (SDIC) if there exists a $\delta > 0$ such that for every $u \in U$ and in every neighborhood of $u \in U$ there exists a $v\in{U}$ and an integer $N:=N{(u,v)}\in\mathbb{Z}$ such that $d(T^Nu,T^Nv)>\delta$. 	
\end{Definition}

@@

\begin{Definition}
  [\bf {Topologically Transitive}]\label{Dfn_TopolTrans}\rm
	A dynamical system $F: U \to U$ is topologically transitive if for any pair of nonempty open sets $E_1$ and $E_2$ there exists a $n\in\mathbb{N}$ such that $T^n(E_1) \cap E_2 \not= \emptyset$. 
\end{Definition}

@@

\begin{Definition}
  [\bf {Meager Set}]\label{Dfn_Meager Set}\rm
A subset of a topological space $U$ is said to be a meager set if it can be written as a countable union of sets of with empty interior. The complement of the a meager set is set to be a residual set.
\end{Definition}

@@

We may now define the notion of Chaos as formulated by Devaney\cite{devaney2018introduction}.
\begin{Definition}
  [\bf {Devaney's Chaos}]\label{Dfn_ChaosDec}\rm
	A dynamical system $T: U \to U$ is said to exhibit chaos in the sense of Devaney if it satisfies the three properties:
	\vspace{-5mm}
  \begin{enumerate}
		\item $T$ has SDIC.
		\item $T$ is topologically transitive.
		\item The set of periodic points of $T$ are dense in $U$. 
	\end{enumerate}
\end{Definition}

@@

\begin{Definition}\rm  
  [\bf {Conjugacy \& Semi-Conjugacy}]\label{Dfn_Conjugate}\rm
  Consider the dynamical systems $T:U\to{U}$, $S:V\to{V}$ and suppose the relationship $\phi \circ T=S\circ \phi$ holds. If $\phi:U\to{V}$ is a homeomorphism, then $S$ is said to be conjugate to $T$ and $\phi$ is called a conjugacy. If we relax the criterion on $\phi$ and merely require $\phi$ to be continuous and surjective where $\phi:U\to{V}$, then $\phi$ is a semi-conjugacy between $T$ and $S$ where T has domain $U$ and S has domain $V$; S is said to be semi-conjugate to T. 
\end{Definition}

@@

We define first the concepts of homeomorphism and embedding:
\begin{Definition}\rm
  [\bf {Homeomorphism}]\label{Dfn_homeo}\rm
  A homeomorphism is a function $f:Z\rightarrow Y$ between two topological spaces $Z$ and $Y$ that is continuous, bijective and has a continuous inverse. 
\end{Definition}

\begin{Definition}
  [\bf {Embedding}]\label{Dfn_embed}\rm
  Consider a homeomorphism $f:Z\rightarrow Y$ for $Y\subset X$. $Z$ is said to be embedded in $X$ by $f$.
\end{Definition}

@@

% \ednote{M: You can omit the theorem, and just say it is a uniform attractor in the nonautonomous dynamical systems literature \cite{Manju_Nonlinearity}, and say the discussion on nonautonomous attractors is beyond the scope of the thesis.}
% Paraphrased.
 In our context, $g$ having the USP is equivalent to $g$ being a topological contraction \cite{manjunath2021universal}, or alternatively that $g$ exhibits the Echo State Property (ESP).

This property is used to describe the concept of fading memory or memory-loss in the majority of literature within the field reservoir computing (RC) \textbf{(Citation)}. 
$g$ having the ESP guarantees that the entire left-infinite history of an input will determine exactly the current system state; there is only ever the possibility of a single reachable state at a given instance of time \cite{jaeger2001echo}
The ESP is also often discussed in terms of a stability property that holds for all inputs of a system~\cite{manjunath2020stability} and, furthermore, plays a key role in the design and training of recurrent neural networks within the field of RC \cite{Manju_ESP}.

Defined formally, the ESP is intrinsically linked to an input (see \cite{Manju_ESP}) Unfortunately, definitions and results concerning the ESP do not have much practical use since a relationship of the network's response to the temporo-statistical properties of the input is not directly described. A more detailed presentation may be found in~\cite{jaeger2001echo}.

\section{Next section? \ednote{I feel a break is necessary here, but would hear from you what your thoughts are.}}

Having already defined the reachable set $X_U$, we now pause for a moment to fix additional notation.
Letting $\cev{u}^{n}:=(\ldots,u_{n-2} ,u_{n-1})$ be the left-infinite subsequence of an input, $\overleftarrow{U}$ then denotes all these left-infinite sequences in $U$. 
Moreover, $\cev{u}^{n}v:=(\ldots,u_{n-2} ,u_{n-1}, v)$ is to symbolise the input up to time $n$ with $v \in U$ being the specific input value at time $n$. 
The introduction of a new input at time $n$ can be described by a mapping $\sigma_v:   \cev{u}^{n} \mapsto \cev{u}^{n}v$.

@@

  Continuing to refine our attention, we proceed to consider a specific subclass of conjugacies.

@@

\begin{Definition}
  [\bf Causal Mapping]\label{Def_CausMap}
  A continuous, surjective map $H:\overleftarrow{U}\to\overleftarrow{X}_U$ such that \[H\circ\tilde{g}_v=\sigma\circ{H}\] where $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
\end{Definition}

@@

\textbf{We direct our attention to the function $H_2(\overline{u}):=(h(r\overline{u}, h(\overline{u})))$. }

@@

\section{Numerical simulations}
In this section we showcase numerical results pertaining to 3 attractors that were simulated using the methodology described in the previous chapters. We first consider a simple physical system.
\subsection{Double Pendulum}

@@

The system has four variables: angle and angular velocity of each pendulum rod. An ideal system is assumed where the rods are massless and no friction in the pivots are considered.
The scalar equations of motion are derived using Newtonian physics and can be found in \cite{DPFormulas}. The second-order system is converted to a first-order ODE and solved using the Runge-Kutta numerical method.

@@

\subsubsection{Thomas' Cyclically Symmetric Strange Attractor}
Thomas' Cyclically Symmetric Strange Attractor, a 3D attractor proposed in 1999 by Ren\'e Thomas in \cite{ThomasAttractor}, is described by a set of three equations which is distinctly reminiscent of the Lorenz system, another deterministic three-equation model exhibiting chaotic behaviour.It has a single parameter $\beta$ and has been shown to transition to chaotic behavious when $\beta<0.208186$~\cite{Thomas_BetaParameter}.
\begin{eqnarray}\label{eqns_thomas}
  x_{n+1} = \sin(y_n) - \beta{x_n} \\
  y_{n+1} = \sin(z_n) - \beta{y_n} \\
  z_{n+1} = \sin(x_n) - \beta{z_n}
\end{eqnarray}

The behaviour of the system with a $\beta$-parameter value of 0.1056 is simulated by scaling it to fit inside the interval $[-1,1]$ and both perturbed with noise as well as leaving it intact. Specifically the noise is obtained from a normally distribution with mean 0 and standard deviation 0.05, which translates approximately to *dB.
 A sequence of 3000 observations in the clear and noisy data-set respectively is fed into the system with 300 entries discarded before predicting the next 9000 entries.

\begin{figure}[ht]
  \centering
  \minipage{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{Thomas_nonoise.eps}
    \caption*{True and predicted trajectories in the absence of noise.}
  \endminipage\hfill
  \minipage{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{ThomasNoisy.eps}
    \caption*{True and predicted trajectories for noise added.}
  \endminipage
\end{figure}

The RNN was initialised as follows: The dimension of the network is set equal to 500 neurons and 12 hidden layers of dimension 64 each were initialised. Training is realised through 150 epochs of batch sizes of 128 each; the map is learnt via the Adam Optimiser using finer and finer learning rates (0.001 and then divided by 10 at every iteration).

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.35]{Thomas_1.eps}\caption*{Predicted trajectories for the attractor demonstrate empirically the ability to predict the evolution of the trajectory for the next ~100 timesteps}
  \includegraphics[scale=0.5]{Thomas_3.eps}\caption*{Represented here the learnt (blue) and actual (red) densities of the first coordinate of the dataset.}
\end{figure}

\subsubsection{Fractal Dream Attractor}

Another 2-equation discrete-time map named the Fractal Dream Attractor, or more commonly known as the Pickover Map (first discovered by Clifford A. Pickover and discussed in his fascinating book "Chaos in Wonderland"\cite{PickoverChaos}), was also considered.
\begin{eqnarray}\label{eqns_clifford}
  {x_{n+1}=\sin(ay_n) + c\cos(ax_n)} \\
  {y_{n+1}=\sin(bx_n)+d\cos(by_n)}
\end{eqnarray}

\begin{figure}[ht]
  \centering
  \includegraphics[width=1.0\textwidth,left]{Clifford_1.eps}
  \caption*{These graphs were constructed by predicting the Clifford system 15000 steps into the future and in so doing illustrating the long-term consistency and accuracy of the learnt system. As perceived here, we are able to lock on to the trajectory of the Clifford map almost exactly for the first 25 steps.}
  \minipage{0.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{Clifford_2.eps}
  \endminipage\hfill
  \minipage{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{Clifford_3.eps}
  \endminipage
  \caption{The bottom row, left, shows a plot of the true attractor(red) and the predicted values(blue). Bottom row, right, shows the distribution of the first coordinate of the learnt system (blue) and the actual Clifford system (red). }
  \label{Fig_Clifford}
\end{figure}

\section{Generalized Pearson Correlation}
\ednote{B: Need to change heading here.}

\textbf{Pearson Introduction}

@@

          \hline
          $(w_n)$ comes from the Clifford Attractor \\ (for $a = -1.7; b = 1.8; c = -1.9; d = -0.4$): & & & \\
        {$w_{n+1}= \begin{bmatrix} \sin(aw_{n,y}) + c\cos(aw_{n,x}) \\ 
                                                                    \sin(bw_{n,x})+d\cos(bw_{n,y}) \end{bmatrix}$} & & & \\
          \multirow{3}{*}{$u_n = w_n-\overline{w}$}
              & 10 & -0.21713 & 0.78719 \\
              & 100 & &  0.8334 \\
              & 1000 & & 0.84854 \\
          \hline  
          \hline 
          $(w_n)$ comes from the Logistic map: & & & \\
          {$ w_{n+1}  = 4w_n(1-w_n)$} & & & \\
          \multirow{3}{*}{$u_n = w_n - 0.5$} 
              & 10 &-0.0314  & 0.5577\\
              & 100 &  & 0.7150\\
              & 1000 & & 0.7826\\
          \hline
          \hline
          $(w_n)$ comes from the Svensson Attractor \\ (for $a = -1.7; b = 1.8; c = -1.9; d = -0.4$): & & & \\
          {$w_{n+1}= \begin{bmatrix} d\sin(aw_{n,x}) - \sin(bw_{n,y}) \\ 
                                                                      c\cos(aw_{n,x})+\cos(bw_{n,y}) \end{bmatrix}$} & & & \\
            \multirow{3}{*}{$u_n = w_n-\overline{w}$}
                & 10 & -0.2243 & 0.49698 \\
                & 100 & &  0.63310 \\
                & 1000 & & 0.71151 \\
          \hline
          \hline
          $(w_n)$ comes from the DP \\ (for ): & & & \\
          \multirow{3}{*}{$u_n = w_n-\overline{w}$}
                & 10 & 0.99141 & 0.98916\\
                & 100 & &  0.99238 \\
                & 1000 & & 0.99278 \\
          \hline        
      \end{tabular}} %\ednote{http://paulbourke.net/fractals/peterdejong/}

      \caption{Multidimensional Correlation Coefficients $\rho$ to indicate a general reduction in the functional complexity of the map $G_T$ that arises from a RNN. Each row corresponds to a different dynamical system used in the experiments in \cite{Main_article}. In the second column corresponds to the dimension of $X$ (number of artificial neurons) in the RNN used. 
      The numerical estimate of $\rho$ for the relevant vectors is plotted in the last two columns. The reader can compare the linear relationship between $u_n$ vs $T(u_{n})$ and the linear relationship $\begin{bmatrix}
              x_{n-1}\\
              x_n
          \end{bmatrix}$ vs $G_T \left( \begin{bmatrix}
              x_{n-1}\\
              x_n
          \end{bmatrix}\right)$. The dimension of the RNN from \eqref{Seq_RNN} is also given, showcasing that increasing the dimension of the driven system typically yields a map $G_T$ of lower functional complexity.} \label{Table_FC}
      \end{table}\label{tbl_attractorsPearson}
\end{center}
